Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-03-31 WSSSPE1_report/WSSSPE1_summary_report.tex
Summarized paper 1 in Implementing Policy.

% First, Krintz et al from The University of California at Santa Barbara’s Department of Computer Science discuss one of these important issues: developing systems for API governance.

% The authors make the point that scientific research is moving away from local hardware environments towards cloud computing. 
% Therefore, instead of focusing on access to hardware, we will need to focus on access to the digital assets: the code and the data. 
% APIs—programming interfaces—are the main link governing interactions between these assets.
% Because APIs are the main interface between different digital assets, they have to be maintained in a sustainable way.

% The authors focus on understanding the portability and consistency of APIs used to connect these data archives, 
% because changes in APIs affect accessibility of data. 
% They define two different types of compatibility, 
% semantic compatibility and 
% syntactic compatibility. 
% They demonstrate an algorithmic method for categorizing a particular API port as “hard” or “easy,” at least for semantic compatibility.

>>>>

Krintz et al~\cite{Krintz_WSSSPE} describe how in an era in which computing more and more frequently takes place in a distributed cloud, the control over digital assets is increasingly shifting from physical infrastructure to APIs, in particular web-service APIs. Yet, as Krintz et al observe, although science communities have  typically developed solid practices for managing physical IT infrastructure in data centers, corresponding practices and technology for API governance, refered to by Krintz et al as the ``combined policy, implementation, and deployment control'', is far less developed. As Krintz et al demonstrate, APIs to digital assets can and do change, sometimes quite frequently. raising the need to port dependent applications. The effort required for porting is notoriously difficult to estimate, making it nearly impossible for IT organizations to assess and thus properly manage their impact. To address this, Krintz et al propose a mechanism that evaluates the porting effort between two versions of a web-service API in a formal and automated way. To analyze the porting effort, their method divides API changes into \emph{syntactic similarity}, the changes in inputs and outputs, and into \emph{semantic similarity}, the changes in the API's behavior. In initial tests, the method showed good congruence with human developers in scoring porting effort, offering the potential that API governance can become as solid a part of scientific IT management as data center infrastructure management is today.
